### 2022-02-25 doc/contrastive-learning.tex

\subsection{Experiments}

@@

>>>>

\subsection{Experiment log}

@@

\subsubsection{25.02.2022 - Image Contrastive learning}

\textbf{Details:} Instead of using a BYOL loss with only positive samples, I went back to the old contrastive loss and was able to see a much more normal loss curve. Visualizing the results shows that it has learned key features in the images.

\textbf{Results:} Here are some sample visualizations:

\begin{figure}[h!]
    \begin{center}
        \includegraphics[scale=0.4]{images/experiments/25.02.2022-image-pretrain-vis1.png}
        % \caption{Visualization of pre-trained image features}
    \end{center}
\end{figure}

\begin{figure}[h!]
    \begin{center}
        \includegraphics[scale=0.43]{images/experiments/25.02.2022-image-pretrain-vis2.png}
        % \caption{Visualization of pre-trained image features}
    \end{center}
\end{figure}

\begin{figure}[h!]
    \begin{center}
        \includegraphics[scale=0.35]{images/experiments/25.02.2022-image-pretrain-vis3.png}
        % \caption{Visualization of pre-trained image features}
    \end{center}
\end{figure}

\newpage
